---
title: "BA Group Project"
output:
  html_document: default
  pdf_document: default
  word_document: default
date: "2022-12-01"
---
# Part 1 : Churn Data
# Loading the required Libraries that are required for the Project.
```{r}
library(readr)
library(tidyverse)
library(caret)
library(gmodels)
library(rpart)
library(pROC)
library(rattle)

```

# Importing the Churn Dataset that is given to us.
```{r}
Given_Churn_Datafile= read.csv("C:/Users/Pavan Chaitanya/Downloads/Churn_Train.csv")

```

# Examinig the details regarding the data file.
```{r}
# Head Part of the Data file
head(Given_Churn_Datafile)

#Summary of the Data present in the data file.
summary(Given_Churn_Datafile)

#Data Types of Data Columns in the Data file
str(Given_Churn_Datafile)

#Glimpse of the Data Given to us
glimpse(Given_Churn_Datafile)

```

# Data Type Conversion.
```{r}
# Converting the Char type data to factors for our convience
Given_Churn_Datafile = Given_Churn_Datafile %>% mutate_if(is.character, as.factor)

```

# Checking where the data conversion is sucessful or not.
```{r}
str(Given_Churn_Datafile)
```

# Checking for the NA values if they are present in the dataset .
```{r}
colSums(is.na(Given_Churn_Datafile))

```

# Checking for the Negative Values if they are present in dataset by columns wise.
```{r}
sapply(Given_Churn_Datafile %>% select_if(is.numeric), function(x) {
                                                                      sum(x < 0, na.rm = TRUE)
                                                                    })
Given_Churn_Datafile =
  Given_Churn_Datafile %>% mutate_if(is.numeric, function(x) {
                                                                  ifelse(x < 0, abs(x), x)
                                                              })
# We see that account_length and number_vmail_messages have some Negative values and we cannot remove them because they are connected to the final Churn Variable.
```

# To deal with NA Values that are present in the data and removing from the data set. 
```{r}
# We are following the MedianImpute as a Method to dela with the NA Values in the Dataset 
NA_Dealing_Model= preProcess(Given_Churn_Datafile %>% select_if(is.numeric),method = "medianImpute")
Predict_Data = predict(NA_Dealing_Model, Given_Churn_Datafile %>% select_if(is.numeric))

Given_Churn_Datafile = Given_Churn_Datafile %>% select(setdiff(names(Given_Churn_Datafile), names(Predict_Data))) %>% cbind(Predict_Data)

# Viewing the Datafile with no NA Values
view(Given_Churn_Datafile)

# Checking Finally wether there are any NA Values Present in the each Column of the dataset.
colSums(is.na(Given_Churn_Datafile))
```
# Visualization of the Data present in the Dataset
```{r}
# Numeric Values Distribution Plot
Given_Churn_Datafile %>% select_if(is.numeric) %>% mutate_all(scale) %>% gather("features","values") %>% na.omit() %>% 
  ggplot(aes(x = features, y = values)) +
  geom_boxplot(show.legend = FALSE) +
  labs(x = " Numeric Variables") +
  ggtitle(label = "Numeric Values Distribution")
```

```{r}
# Churn Variable Visualization
ggplot(Given_Churn_Datafile, aes(x=churn, y=..prop..,group = 2)) + 
  geom_bar(fill="Red") +
    geom_text(aes(label=round(..prop..,1)),stat = "count",
            position = position_stack(vjust=0.8)) + 
  scale_x_discrete(labels = c("Not Churned","Yes Churned"))

# From the Plot we can see that 90 % hasn't churned but 10 % churned.
```
# Adding the State and Churn Variables to the Updated Churn Dataset for our calculations.
```{r}
str(Given_Churn_Datafile) # Without Updation
Given_Churn_Datafile = Given_Churn_Datafile %>% select(-state, -churn) %>% 
  fastDummies::dummy_cols(., remove_selected_columns = TRUE) %>% mutate(state = Given_Churn_Datafile$state, churn = Given_Churn_Datafile$churn)
str(Given_Churn_Datafile) # With Updation
```

# Model Strategy

# we are following the Decesion tree  as our Model beacuse we believe that to illustrate the influence of numerous variables and their significance in forecasting the result of the target variable , so we will go with Decision Tree approach.

# So preprocessing of Data:
```{r}
# Splitting  the dataset into training set(75%) and validation set(25%).
set.seed(5454)
Data_partition<- createDataPartition(Given_Churn_Datafile$churn, p=0.75, list=FALSE)
Req_Churn_Data_train = Given_Churn_Datafile[Data_partition,]
Req_Churn_Data_test = Given_Churn_Datafile[-Data_partition,]

```

# Scaling the Preprocessed Data
```{r}
PreProcess_Scale <- preProcess(Req_Churn_Data_train %>% select_if(is.numeric), method = c("center", "scale"))
Req_Churn_Data_train_norm <- predict(PreProcess_Scale, Req_Churn_Data_train %>% select_if(is.numeric))
Req_Churn_Data_test_norm <- predict(PreProcess_Scale, Req_Churn_Data_test %>% select_if(is.numeric))

Req_Churn_Data_train_norm$churn <- Req_Churn_Data_train$churn
Req_Churn_Data_test_norm$churn <- Req_Churn_Data_test$churn
```

# Model Construction
```{r}
# Using Rplot
DecisionTree_Model <- rpart(churn ~ ., data = Req_Churn_Data_train_norm, method = "class")
summary(DecisionTree_Model)
plot(DecisionTree_Model)
text(DecisionTree_Model)
print(DecisionTree_Model)


# Using fancyRpartPlot
fancyRpartPlot(DecisionTree_Model)
```
```{r}

```
# Model Building is done and we can intrepret the results.
```{r}
# Predicting values using based on DecisionTree_Model.
pred_labels <- predict(object = DecisionTree_Model,Req_Churn_Data_test_norm, type = "class")
pred_probs <- predict(object = DecisionTree_Model,Req_Churn_Data_test_norm)

# Performance Metrics
# Confusion matrix for the DecisionTree_Model.
CrossTable(x=Req_Churn_Data_test_norm$churn, y = pred_labels, prop.chisq = FALSE)
confusionMatrix(pred_labels,Req_Churn_Data_test_norm$churn)

# From the confusion Matrix we can say that 

# Accuracy ~ 0.93
# Sensitivity ~ 0.95         
# Specificity ~0.6
```

# AUC of the  Model
```{r}
roc(Req_Churn_Data_test$churn, pred_probs[,2])

# As AUC is greater than 0.8 we can say that the model is good.

# Plotting the AUC of the Model
plot.roc(roc(Req_Churn_Data_test$churn, pred_probs[,2]))
```
# Part 2 : Predicting for Customers_To_Predict
```{r}
# We need to use load() to read the RData file
load("C:/Users/Pavan Chaitanya/Downloads/Customers_To_Predict.RData")
Customers_To_Predict_data  <- Customers_To_Predict
Customers_To_Predict <- Customers_To_Predict %>% select(-state) %>% fastDummies::dummy_cols(., remove_selected_columns = TRUE)
Customers_To_Predict <- as.data.frame(scale(Customers_To_Predict))
predict_labels <- predict(object = DecisionTree_Model, Customers_To_Predict, type = "class")

# Adding the New Predicting column to the Customer_To_Predict Datafile.
Customers_To_Predict <- Customers_To_Predict_data %>% mutate(Churn_Prob = predict_labels)

# Viewing the Updated Data File
View(Customers_To_Predict)

#Head Part of the Updated Data file
head(Customers_To_Predict)

#Printing only the Churn_Prob Column
print(Customers_To_Predict$Churn_Prob)

#Displaying the count of Yes/No Present in Churn_Prob Column.
table(Customers_To_Predict$Churn_Prob)

```
